Compact Core Galaxies in the RESOLVE Survey

### 2016-05-13 paperdraft.tex
almost done!

\documentclass[iop,apj]{emulateapj}
\pdfoutput=1 %for arxiv submission to use pdf
\usepackage{apjfonts}
\usepackage{natbib}
\usepackage{epstopdf}
\usepackage{gensymb}
\usepackage{longtable}
\usepackage{amsmath,amstext,textcomp}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
\usepackage[all]{hypcap} %Links go to figures. This breaks deluxetables; use \capstartfalse \capstarttrue around deluxetables to fix it.
\renewcommand{\sectionautorefname}{\S} %for \autoref
\renewcommand{\subsectionautorefname}{\S} %for \autoref
\renewcommand{\subsubsectionautorefname}{\S} %for \autoref

@@

\title{Compact Core Galaxies in the RESOLVE Survey}
\author{Elaine M. Snyder\altaffilmark{1}}
\author{Sheila J. Kannappan\altaffilmark{1}}
\author{Dara J. Norman\altaffilmark{2}}
\author{Ashley S. Bittner\altaffilmark{1}}
\author{Mark A. Norris\altaffilmark{3}}
\author{Kathleen D. Eckert\altaffilmark{1}}
\author{Ian Dell'Antonio\altaffilmark{4}}
\author{Callie Hood\altaffilmark{1}}
\author{Samantha Dallas\altaffilmark{4}}
\author{David V. Stark\altaffilmark{1}}
\author{Amanda J. Moffett\altaffilmark{1,5}}
\author{the RESOLVE Team}
\affil{$^1$Department of Physics and Astronomy, University of North Carolina, 141 Chapman Hall CB 3255, Chapel Hill, NC 27599, USA; emsnyder@live.unc.edu}
\affil{$^2$National Optical Astronomical Observatory, 950 N Cherry Ave, Tucson, AZ 85719, USA}
\affil{$^3$Jeremiah Horrocks Institute, University of Central Lancashire, Preston, PR1 2HE, United Kingdom}
\affil{$^4$Department of Physics, Brown University, Box 1843, 182 Hope Street, Barus \& Holley, Providence, RI 02912} 
\affil{$^5$International Centre for Radio Astronomy Research (ICRAR), The University of Western Australia, 35 Stirling High-
way, Crawley, WA 6009, Australia}
\begin{abstract}
We analyze the complete set of 96 ``compact core galaxies'' (CCGs) in the volume-limited RESOLVE survey to investigate their formation and evolution in relation to compact galaxies such as ultra compact dwarfs (UCDs), compact ellipticals (cEs), and dwarf ellipticals (dEs) across a broad statistical distribution of environments. To identify CCGs, we use \textsc{Galfit} to perform one- and two-component S\'ersic fits for all galaxies in RESOLVE with UKIDSS $Y$-band imaging (98\% of the survey), which produces seeing-deconvolved effective radius (\Reff) measurements. The one component fits are used to select candidate CCGs with \Reff\ $< 1000$ pc, and we then perform new two component fits to these galaxies with the S\'ersic n of the second component held fixed at 1 for an exponential disk. We finalize the CCG sample by selecting on core-only (first component) \Reff\ $<800$pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog. We quantify the amount of light in the core and envelope of each CCG by taking the logarithm of the ratio of the light in each component. The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated. With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars. We find that CCGs naturally occur in a range of environments from free floating to cluster. We also derive velocity dispersions ($\sigma$) for 8 CCGs from Gemini IFU data and SOAR spectroscopy. Comparing to other RESOLVE galaxies and AIMSS cEs/dEs, we search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping (as expected for cEs) or dissipative formation (as expected for dEs), respectively. Initial results show 4 CCGs likely following the dissipative formation track and 4 CCGs that are intermediate.

@@

CSSs have half-light radii (\Reff) ranging typically from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple ideas for how they form. The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}. The is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Norris2011, Jennings2015, Zhang2015}. \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs. Similarly, cEs are thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}. More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole. On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as during mergers or in the two-phase formation process detailed in \citet{Oser2010}. One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that all of the above scenarios for UCD and cE formation occur.

In contrast to CSSs, dwarf elliptical galaxies \citep[dEs;][]{Sandage1985} and their nucleated counterparts \citep[dE,Ns;][]{Binggeli1984} are quite common, especially in clusters where they were first discovered. In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles. While dEs are typically larger than CSSs with \Reff\ ranging from $\sim600$~pc up to $\sim2000$~pc \citep[e.g.,][]{Norris2014}, the cores of dE,Ns can reach down to CSS-like sizes and reside within larger envelopes that are dE-sized. Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevic2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}. They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that have been ram-pressure stripped and quenched as they enter the cluster environment \citep{Lisker2013, Crawford2016a}. There is also evidence that dE,Ns become UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.

Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with core \Reff\ up to 800~pc. The goal of this paper is to study these galaxies as part of a continuum of compact galaxies in order to differentiate between formation scenarios. Clues to how CCGs form may be given by their environments,  morphology i.e., one- or two-component structure, star formation histories, and kinematics. We highlight these data below.

%environments
\textit{Environments.} CSSs have been found in a large range of environments thus far. UCDs were first discovered in the Fornax cluster \citep{Hilker1999, Drinkwater2000} and have since been found in the cores of several other clusters \citep{Price2009,Madrid2010,Jones2006,Mieske2009,Misgeld2008}, in groups \citep{Evstigneeva2007}, and near field galaxies \citep{Hau2009,Norris2011}. M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs have later been found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}. As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016a}, but have also been found near groups \citep{Crnojevic2014,Penny2014}. Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013} and \citet{Paudel2014} both find one cE separated from other galaxies by $\sim~840$ and $\sim~600$~kpc, respectively.

Environment bears on formation scenarios in different ways. One possibility is that CSSs found in group or cluster environments may be tidally stripped remnants, whereas free floating CSSs may rather be dissipatively formed like Es. However, \citet{Chilingarian2015} argue that these free-floating cEs could actually be tidally-stripped cores that are ejected from groups and clusters during the tidal stripping process. The recent discovery of a free-floating GC and UCD that have likely been tidally stripped in \citet{Sandoval2015} supports this idea.

%structure
\textit{Morphologies.} CSSs have been found to exhibit either one component (i.e., just a core) or two component (i.e., a core plus a surrounding envelope of gas and stars) morphology. \citet{Graham2002} have shown that M32's light profile is best fit with a core plus a surrounding exponential disk profile, which they argue points toward a tidal-stripping origin. \citet{Pfeffer2013} use N-body simulations to predict that UCDs that are tidally stripped remnants will also display multi-component surface brightness profiles due to lingering outer galaxy structures. Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center during mergers or the convergence of streams of cold gas and star formation begins. This core is then ``puffed up'' through time as it interacts with other galaxies. The free-floating cE discovered in \citet{Huxor2013}, shown to have only a one-component light profile, may be an example of the first step in this two-phase formation. It's important to note that these effects may vary based on the degree of stripping and how much time has passed since the stripping or dissipative formation occurred.

By their nomenclature, dEs and dE,Ns have already been divided into one and two component morphologies. Studies have found that dE,Ns are usually more common than dEs: \citet{Grant2005} find that the majority of Virgo cluster dwarfs are indeed nucleated and speculate that at least some of the nuclei were formed out of an existing non-nucleated galaxy from infalling gas. Another possibility is that the morphology is already in place as dEs/dE,Ns form: \citet{Mastropietro2005a} use N-body simulations to show that as the progenitors of dEs/dE,Ns enter clusters, their morphologies are greatly disrupted but disks may not be completely destroyed by ram pressure or tidal stripping, leaving the dEs/dE,Ns we observe today.

@@

For dEs and dE,Ns, there is similar diversity in colors. \citet{SmithCastelli2012} find dEs in the Antlia cluster with both red and blue colors. \citet{Drinkwater2000} and \citet{Ferrarese2006} study the colors of dE,Ns and find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies. \cite{Grant2005} also find that two-fifths of the Virgo dE,Ns have young cores compared to their envelopes, while three-fifths display the opposite trend.

@@

  We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.  AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies and in groups and clusters, and includes both previously known and newly discovered objects. The AIMSS CSS discovery process was as follows. First, a search was conducted in the HyperLeda redshift catalog \citep{Paturel2003} for all galaxies with M$_{\rm B}~<~-15$ and distances between $\sim 7$ and 200 Mpc (close enough to ensure any CSSs with \Reff\ $> 50$ pc would be resolved in any available HST imaging). The team then searched the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150 kpc in projection of the selected galaxies. Next, Source Extractor was run on the HST images, and candidates were identified using a training set of previously known CSSs from the literature. After vetting by eye and cross-matching to ensure none are previously known, spectra were obtained for redshift confirmation and measurements of velocity dispersions. AIMSS also includes literature data for previously known UCDs, cEs, dEs, dE,Ns, dwarf spheroidals, dwarf S0s, young massive clusters, and Es. The catalog provides a compilation of absolute $V$-band magnitude, stellar mass, half-light radius, and velocity dispersion for each of its objects. Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can compare our CCGs. We also note that the objects in AIMSS are not decomposed, meaning their \Reff\ are all single component fits. We discuss this more in \autoref{discussion}.

\begin{figure*}[b]
\begin{center}
\includegraphics[scale=0.5]{galfitexample.eps}
\caption{Model inputs and outputs from \textsc{Galfit}. The left column shows the UKIDSS $Y$-band image cutout around the galaxy. The middle column shows the best fit \textsc{Galfit} model, and the right column shows the residuals (data-model). The top row shows the one component fit for one of the RESOLVE galaxies, rf0055. As seen in the residual image, the model is overfitting the inner bulge, and underfitting the outer envelope. The bottom row shows the two component fit for the same galaxy. We are now  able to fit both the inner bulge and the outer envelope. The residual is much cleaner, although there may be some spiral structure remaining.}
\label{fig:galfit}
\end{center}
\end{figure*}

@@

\item[The initial input file]{The initial input file gives \textsc{Galfit} the file paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters. For the one component fits, we set up our input file to include a section to measure the level of the sky background and another section to fit a S\'ersic profile \citep{Sersic1963, Sersic1968} to the galaxy. The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle. These initial values for these parameters can just be rough guesses, but for our purposes, we use values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's custom processed photometric data (see \autoref{phot} for more details).}

\item[Imaging data]{We use publicly-available high resolution $Y$-band imaging from the UKIDSS Large Area Survey \citep{Lawrence2007}. This data set was chosen because it covers both RESOLVE-A and RESOLVE-B and offers $\sim0.8''$ seeing resolution corresponding to $\sim350$pc at RESOLVE distances in turn letting us span down to the sizes of cE-like galaxies. The $Y$ band is advantageous too, since it probes the underlying stellar population and will not skew our measurements to larger radii if the galaxy is currently experiencing a starburst. We download $\sim10'\times10'$ images of each galaxy from the WFCAM Science Archive\footnote{\url{was.roe.ac.uk//}}}. While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful when constructing the PSF image. There are only 25 galaxies in RESOLVE (2\% of the survey) that do not have UKIDSS imaging and thus are excluded from our analysis.

\item[The PSF image]{\textsc{Galfit} uses the PSF image to deconvolve the galaxy light profile from the seeing, thereby removing the effects of atmospheric scattering of the galaxy light as the data was taken. We build our PSF image via the following steps.
\begin{enumerate}

@@

  We use all of the above to obtain a one component, seeing-deconvolved fit for every galaxy in the RESOLVE survey. We then perform the two component fits as follows. We use the output of the one component fit as the basis of the input file for the two component fit. The first two sections in the two component fit initial input file will be identical to the output of the one component fit (except that the names of the files to be output are changed). We then add a third section to include a second S\'ersic fit, and change the initial guess for \Reff\ to be double that of the one component best fit. This gives \textsc{Galfit} an idea to fit on both a core and envelope. The PSF, image, and mask image will all be the same as before. We add to the constraint file the same constraints as listed in \autoref{constrtable}, but for the third section. In other words, there will be two sets of constraints in the file now, with the first set applying to the first S\'ersic fit and the second set applying the second S\'ersic fit. The constraints for each parameter are the same for both sets. We do not further constrain the two component fits since we are looking for general fits to the wide variety of galaxies in RESOLVE and do not want to over-constrain the fits.

For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle as well as the $\chi^2$, $\chi^2/\nu$ and number of degrees of freedom for the fit. Also output is a fits file that contains the data, best fit model, and residual images. See \autoref{fig:galfit} for example one and two component fits for the RESOLVE galaxy rf0055.

@@

\begin{figure*}[hbpt!]
\begin{center}
\includegraphics[scale=0.65]{coretoenvelopeims.eps}
\caption{Five of the 96 CCGs in the final sample arranged in order from envelope-only to core+envelope to core-only. Images are taken from the SDSS-DR8 image list tool. The galaxy rf0250 is an example of one of eleven CCGs that was fit with a large diffuse envelope and has hence been reclassified as ``core-dominated''.}
\label{fig:pics}
\end{center}
\end{figure*}

@@

We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$~pc. Since we are looking for galaxies with compact cores, extending to \Reff\ $\sim 1000$~pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit. We do note that this limit is arbitrary, and will be relaxed in the future to allow CCGs with larger envelopes be included in the sample (see \autoref{conclusions}). We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are normally spiral or irregular galaxies. After this selection, we are left with 124 galaxies in the CCG candidate sample.

Next, we perform new two component fits using different fitting constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic component fit is constrained to always be larger than that of the first S\'ersic component fit, and (3) the S\'ersic n of the second component is held constant at 1 representing an exponentially decreasing disk profile. We let the values of \Reff, integrated magnitude, b/a ratio, and PA change for both fits. By doing this, we are forcing \textsc{Galfit} to fit on a core (the first S\'ersic component fit) and disky envelope (the second S\'ersic component fit) for each CCG candidate.

@@

We quantify the amount of light in the core vs.~the envelope by taking a ratio of the flux in each component. We compute the fluxes using $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}. We note that \textsc{Galfit} calculates the integrated magnitude for S\'ersic profiles using the equations:

>>>>

\documentclass[iop,apj]{emulateapj}
\pdfoutput=1 %for arxiv submission to use pdf
\usepackage{apjfonts}
\usepackage{natbib}
\usepackage{epstopdf}
\usepackage[final]{pdfpages}
\usepackage{gensymb}
\usepackage{longtable}
\usepackage{amsmath,amstext,textcomp}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
\usepackage[all]{hypcap} %Links go to figures. This breaks deluxetables; use \capstartfalse \capstarttrue around deluxetables to fix it.
\renewcommand{\sectionautorefname}{\S} %for \autoref
\renewcommand{\subsectionautorefname}{\S} %for \autoref
\renewcommand{\subsubsectionautorefname}{\S} %for \autoref

@@

\title{Compact Core Galaxies in the RESOLVE Survey}
\author{Elaine M. Snyder\altaffilmark{1}}
\author{Sheila J. Kannappan\altaffilmark{1}}
\author{Dara J. Norman\altaffilmark{2}}
\author{Ashley S. Bittner\altaffilmark{1}}
\author{Mark A. Norris\altaffilmark{3}}
\author{Kathleen D. Eckert\altaffilmark{1}}
\author{Ian Dell'Antonio\altaffilmark{4}}
\author{Callie Hood\altaffilmark{1}}
\author{Samantha Dallas\altaffilmark{4}}
\author{David V. Stark\altaffilmark{1}}
\author{Amanda J. Moffett\altaffilmark{1,5}}
\author{the RESOLVE Team}
\affil{$^1$Department of Physics and Astronomy, University of North Carolina, 141 Chapman Hall CB 3255, Chapel Hill, NC 27599, USA; emsnyder@live.unc.edu}
\affil{$^2$National Optical Astronomical Observatory, 950 N Cherry Ave, Tucson, AZ 85719, USA}
\affil{$^3$Jeremiah Horrocks Institute, University of Central Lancashire, Preston, PR1 2HE, United Kingdom}
\affil{$^4$Department of Physics, Brown University, Box 1843, 182 Hope Street, Barus \& Holley, Providence, RI 02912} 
\affil{$^5$International Centre for Radio Astronomy Research (ICRAR), The University of Western Australia, 35 Stirling High-
way, Crawley, WA 6009, Australia}
\begin{abstract}
We analyze the complete set of 96 ``compact core galaxies'' (CCGs) in the volume-limited RESOLVE survey to investigate their formation and evolution in relation to compact galaxies such as ultra compact dwarfs (UCDs), compact ellipticals (cEs), and dwarf ellipticals (dEs) across a broad statistical distribution of environments. To identify CCGs, we use \textsc{Galfit} to perform one-component S\'ersic fits for all galaxies in RESOLVE with UKIDSS $Y$-band imaging (98\% of the survey), which produces seeing-deconvolved effective radius (\Reff) measurements. Candidate CCGs are selected to have \Reff~$<~1000$~pc. Two component (core and envelope) S\'ersic fits are then performed on the candidates with S\'ersic n fixed at 1 for an exponential disk profile for the envelope. We finalize the CCG sample by selecting core \Reff~$<~800$~pc, an upper limit that encompasses all of the similarly compact stellar systems (UCDs, cEs) included in the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog. We quantify the morphologies of CCGs by taking the logarithm of the ratio of the light in each component. The result is a smooth continuum of CCGs that range from envelope-dominated to core+envelope to core-dominated, which may represent earlier or later evolutionary stages of CCGs. With GALEX $NUV$, SDSS $ugriz$, and 2MASS/UKIDSS $YJHK$ data, we derive colors and star formation histories and find that a significant number of CCGs live on the blue sequence and have recently formed stars. We find that CCGs naturally occur in a range of environments from free floating to cluster. We derive velocity dispersions ($\sigma$) for eight CCGs from Gemini IFU data and SOAR spectroscopy. Comparing to other RESOLVE galaxies and AIMSS cEs/dEs, we search for CCGs offset to higher or lower dispersion in the dispersion-stellar mass relation, which may indicate tidal stripping (as expected for cEs) or dissipative formation (as expected for dEs), respectively. We classify CCGs as CSS-like (small radius and high dispersion), dE-like (large radius and low dispersion), or crossover (small radius and low dispersion). Initial results show four CCGs are dE-like and four are crossovers.

@@

CSSs have half-light radii (\Reff) typically ranging from $\sim$10--600 pc \citep[e.g.,][]{Norris2014}, and there are multiple theories for how they form. The smaller of the CSSs, UCDs may simply be the high mass extension of the GC population \citep{Drinkwater2000, Mieske2002}. There is also evidence that UCDs are created via the tidal stripping of nucleated dwarf galaxies \citep{Bekki2001, Bekki2003, Norris2011, Jennings2015, Zhang2015}. \citet{Seth2014} find a supermassive black hole at the center of another UCD, providing further evidence of tidal stripping being common for UCDs. Similarly, cEs are thought to be the result of tidal stripping events, as argued for the prototypical cE, M32 \citep{Choi2002, Graham2002, Huxor2011}. More evidence is provided by the discovery of tidal streams near cEs \citep{SmithCastelli2008a,Chilingarian2009} and one cE, studied in \citet{Kormendy1997}, that is believed to host a central massive black hole. On the other hand, \citet{Wirth1984}, \citet{Kormendy2009}, and \citet{Kormendy2012a} argue that cEs are the low mass extension to the normal E population created via dissipative formation in gas rich environments, such as during mergers or the two-phase formation process detailed in \citet{Oser2010}. One of the most successful recent searches for CSSs is the AIMSS catalog \citep{Norris2014}: with many newly discovered UCDs and cEs to examine, the authors argue that all of the above scenarios for UCD and cE formation occur.

In contrast to CSSs, dwarf elliptical galaxies \citep[dEs;][]{Sandage1985} and their nucleated counterparts \citep[dE,Ns;][]{Binggeli1984} are quite common, especially in clusters where they were first discovered. In fact, \citet{Binggeli1991} find that of 225 galaxies present in the center of Virgo cluster, 174 are classified as dEs or dE,Ns based on their surface brightness profiles. While dEs are typically larger than CSSs with \Reff\ ranging from $\sim600$~pc up to $\sim2000$~pc \citep[e.g.,][]{Norris2014}, the cores of dE,Ns are comparable in size to to CSSs and reside within larger envelopes that are dE-sized. Similar to cEs, dEs are often thought to be either tidally stripped remnants \citep{Crnojevic2014} or the low mass extension to elliptical galaxies \citep{Kormendy2012a}. They could also be the remnants of late-type disk galaxies or luminous blue compact dwarfs that were ram-pressure stripped and quenched as they entered the cluster environment \citep{Lisker2013, Crawford2016a}. There is also evidence that dE,Ns become UCDs as they fall deeper into the cluster core and are further stripped \citep{Pfeffer2013,Zhang2015,Liu2015}.

Given the similarities in formation scenarios between CSSs and dEs, we introduce the term ``compact core galaxy'' or ``CCG'' to encompass CSSs and dEs with core \Reff\ up to 800~pc. The goal of this paper is to study these galaxies as part of a continuum of compact galaxies in order to differentiate between formation scenarios. Clues to how CCGs form may be given by their environments,  morphology (i.e. one- or two-component structure), star formation histories, and kinematics. We highlight these data below.

%environments
\textit{Environments.} CSSs have been found in a large range of environments thus far. UCDs were first discovered in the Fornax cluster \citep{Hilker1999, Drinkwater2000} and have since been found in the cores of several other clusters \citep{Price2009,Madrid2010,Jones2006,Mieske2009,Misgeld2008}, in groups \citep{Evstigneeva2007}, and near field galaxies \citep{Hau2009,Norris2011}. M32 was first discovered in our Local Group \citep{Faber1973} near M31, and more cEs were later  found in clusters \citep{Chilingarian2007,SmithCastelli2012,Price2009} and other groups \citep{Huxor2011,Chilingarian2010}. As stated previously, dEs and dE,Ns are common in clusters \citep{SmithCastelli2012,Koo1994,Guzman1996,Crawford2016a}, but have also been found near groups \citep{Crnojevic2014,Penny2014}. Only cEs have been found ``free floating'', meaning there is no host galaxy at all: \citet{Huxor2013} and \citet{Paudel2014} both find one cE separated from other galaxies by $\sim~840$ and $\sim~600$~kpc, respectively.

Environment affects formation scenarios in different ways. One possibility is that CSSs found in group or cluster environments may be tidally stripped remnants, whereas free floating CSSs may rather be dissipatively formed like Es. However, \citet{Chilingarian2015} argue that these free-floating cEs could actually be tidally-stripped cores that are ejected from groups and clusters during the tidal stripping process. The recent discovery of a free-floating GC and UCD that have likely been tidally stripped supports this idea \citep{Sandoval2015}.

%structure
\textit{Morphologies.} CSSs have been found to exhibit either one component (i.e., just a core) or two component (i.e., a core plus a surrounding envelope of gas and stars) morphology. \citet{Graham2002} has shown that M32's light profile is best fit with a core plus a surrounding exponential disk profile, which points toward a tidal-stripping origin. \citet{Pfeffer2013} use N-body simulations to predict that UCDs that are tidally stripped remnants will also display multi-component surface brightness profiles due to lingering outer galaxy structures. Conversely, dissipative processes such as the two-phase formation scenario proposed by \citet{Oser2010} cause cores to form as gas rushes to the center during mergers or the convergence of streams of cold gas. This core is then ``puffed up'' through time as it interacts with other galaxies. The free-floating cE discovered in \citet{Huxor2013}, shown to have only a one-component light profile, may be an example of the first step in this two-phase formation. It is important to note that these effects may vary based on the degree of stripping and the time passed since the stripping or dissipative formation occurred.

By their nomenclature, dEs and dE,Ns have already been divided into one and two component morphologies. Studies have found that dE,Ns are usually more common than dEs: \citet{Grant2005} find that the majority of Virgo cluster dwarfs are indeed nucleated and speculate that at least some of the nuclei were formed out of an existing non-nucleated galaxy from infalling gas. Another possibility is that the morphology is already in place as dEs/dE,Ns form. For example, \citet{Mastropietro2005a} use N-body simulations to show that as the progenitors of dEs/dE,Ns enter clusters, their morphologies are greatly disrupted but disks may not be completely destroyed by ram pressure or tidal stripping, leaving the dEs/dE,Ns we observe today.

@@

For dEs and dE,Ns, there is similar diversity in color. \citet{SmithCastelli2012} find dEs in the Antlia cluster with both red and blue colors. \citet{Drinkwater2000} and \citet{Ferrarese2006} study the colors of dE,Ns and find that the cores of dE,Ns tend to have younger stellar populations compared to their host galaxies. \cite{Grant2005} also find that two-fifths of the Virgo dE,Ns have young cores compared to their envelopes, while three-fifths display the opposite trend.

@@

  We use the Archive of Intermediate Mass Stellar Systems (AIMSS) catalog \citep{Norris2014,Forbes2014,Janz2015} as a reference sample for our CCGs.  AIMSS is a catalog of spectroscopically confirmed CSSs found near field galaxies, in groups, and in clusters, and includes both previously known and newly discovered objects. The AIMSS CSS discovery process was as follows. First, a search was conducted in the HyperLeda redshift catalog \citep{Paturel2003} for all galaxies with M$_{\rm B}~<~-15$ and distances between $\sim 7$ and 200 Mpc (close enough to ensure any CSSs with \Reff\ $> 50$ pc would be resolved in any available HST imaging). The team then searched the Hubble Space Telescope archive for WFCP2, ACS, and WFC3 imaging within 150 kpc in projection of the selected galaxies. Next, Source Extractor was run on the HST images, and candidates were identified using a training set of previously known CSSs from the literature. After vetting by eye and cross-matching to ensure none are previously known, spectra were obtained for redshift confirmation and measurements of velocity dispersions. AIMSS also includes literature data for previously known UCDs, cEs, dEs, dE,Ns, dwarf spheroidals, dwarf S0s, young massive clusters, and Es. The catalog provides a compilation of absolute $V$-band magnitude, stellar mass, half-light radius, and velocity dispersion for each of its objects. Thus, though not a statistically-defined sample, AIMSS provides a useful reference catalog to which we can compare our CCGs. We also note that the objects in AIMSS are not decomposed, meaning their \Reff\ are all single component fits. We discuss this more in \autoref{discussion}.

\begin{figure*}[b]
\begin{center}
\includegraphics[scale=0.5]{galfitexample.eps}
\caption{Model inputs and outputs from \textsc{Galfit}. The left column shows the UKIDSS $Y$-band image cutout around the galaxy. The middle column shows the best fit \textsc{Galfit} model, and the right column shows the residuals (data-model). The top row shows the one component fit for the RESOLVE galaxy, rf0055. As seen in the residual image, the model is overfitting the inner bulge, and underfitting the outer envelope. The bottom row shows the two component fit for the same galaxy. We are now  able to fit both the inner bulge and the outer envelope. The residual is much cleaner, although there may be some spiral structure remaining.}
\label{fig:galfit}
\end{center}
\end{figure*}

@@

\item[The initial input file]{The initial input file gives \textsc{Galfit} the file paths to the image, PSF, mask, and constraint file, and also holds the initial guesses for our fit parameters. For the one component fits, we set up our input file to include a section to measure the level of the sky background and another section to fit a S\'ersic profile \citep{Sersic1963, Sersic1968} to the galaxy. The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle. We use initial values for the magnitude, \Reff, b/a, and PA that are derived from RESOLVE's custom processed photometric data (see \autoref{phot} for more details).}

\item[Imaging data]{We use publicly-available high resolution $Y$-band imaging from the UKIDSS Large Area Survey \citep{Lawrence2007}. This data set was chosen because it covers both RESOLVE-A and RESOLVE-B and offers $\sim0.8''$ seeing resolution corresponding to $\sim350$pc at RESOLVE distances in turn letting us span down to the sizes of cE-like galaxies. The $Y$ band is advantageous too, since it probes the underlying stellar population and will not skew our measurements to larger radii if the galaxy is currently experiencing a starburst. We download $\sim10'\times10'$ images of each galaxy from the WFCAM Science Archive\footnote{\url{was.roe.ac.uk//}}}. While \textsc{Galfit} does not require images this large to operate normally, we choose this size so that there will be more stars in the field of view which is useful when constructing the PSF image. There are 25 galaxies in RESOLVE (2\% of the survey) that do not have UKIDSS imaging and thus are excluded from our analysis.

\item[The PSF image]{\textsc{Galfit} uses the PSF image to deconvolve the galaxy light profile from the seeing, thereby removing the effects of atmospheric scattering of the galaxy light as the data was taken. We build our PSF image via the following steps:

@@

  We use all of the above to obtain a one component, seeing-deconvolved fit for every galaxy in the RESOLVE survey. We then perform the two component fits as follows. We use the output of the one component fit as the basis of the input file for the two component fit. The first two sections in the two component fit initial input file will be identical to the output of the one component fit. We then add a third section to include a second S\'ersic fit, and change the initial guess for \Reff\ to be double that of the one component best fit. This gives \textsc{Galfit} a preliminary guess for the radius of an envelope. The PSF, image, and mask image will all be the same as before. We add to the constraint file the same constraints as listed in \autoref{constrtable}, but for the third section. In other words, there will be two sets of constraints in the file now, with the first set applying to the first S\'ersic fit and the second set applying the second S\'ersic fit. The constraints for each parameter are the same for both sets. We do not further constrain the two component fits since we are looking for general fits to the wide variety of galaxies in RESOLVE and do not want to over-constrain the fits.

For both the one and two component fits, \textsc{Galfit} outputs the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle as well as the $\chi^2$, $\chi^2/\nu$ and number of degrees of freedom for the fit. Also output is a fits file that contains the data, best fit model, and residual images. See \autoref{fig:galfit} for example one and two component fits for the RESOLVE galaxy rf0055.

@@

\begin{figure*}[hbpt!]
\begin{center}
\includegraphics[scale=0.65]{coretoenvelopeims.eps}
\caption{Five of the 96 CCGs in the final sample arranged in order from envelope-only to core+envelope to core-only from left to right. Images are taken from the SDSS-DR8 image list tool. The galaxy rf0250 is an example of one of eleven CCGs that was fit with a large diffuse envelope and has hence been reclassified as ``core-dominated''.}
\label{fig:pics}
\end{center}
\end{figure*}

@@

We start by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$~pc. Since we are looking for galaxies with compact cores, extending to \Reff\ $\sim 1000$~pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit. We do note that this limit is arbitrary, and it  will be relaxed in the future to allow CCGs with larger envelopes be included in the sample (see \autoref{conclusions}). We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals, which are normally spiral or irregular galaxies. After this selection, we are left with 124 galaxies in the CCG candidate sample.

Next, we perform new two component fits using different constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic component fit is constrained to always be larger than that of the first S\'ersic component fit, and (3) the S\'ersic n of the second component is held constant at 1 representing an exponentially decreasing disk profile. We let the values of \Reff, integrated magnitude, b/a ratio, and PA change for both fits. By doing this, we are forcing \textsc{Galfit} to fit on a core (the first S\'ersic component fit) and disky envelope (the second S\'ersic component fit) for each CCG candidate.

@@

We quantify the amount of light in the core vs.~the envelope by taking a ratio of the flux in each component. We compute the fluxes using $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}. \textsc{Galfit} calculates the integrated magnitude for S\'ersic profiles using the equations:
